NFC and burnout in teachers - A replication and extension study

### 2022-07-25 Manuscript/Revision_Letter.Rmd
responded to covariance suggestion

That was an oversight on our part, we have added the degrees of freedom to the Chi Square test statistic.

\Assignment{JZ}

>>>>

That was an oversight on our part, we have added the degrees of freedom to the Chi Square test statistic in the manuscript.
We have also added the analysis code for the demand-resource-ratio model with covariance between DTH, DRL, and DRF to our *Analysis.R* script.
The results indicate that the improvement in fit measures is very marginal: From CFI = .775, SRMR = .173, and RMSEA = .131 (model without covariance) to CFI = .831, SRMR = .091, and RMSEA = .114 (model with covariance).
None of the fit measures indicate good fit.
Therefore, we would like to refrain from including this model as yet another exploratory/supplementary analyis.
